\chapter{Background of First User Study} 
\label{sec:first-iteration-scenarios}

%Anything that does not directly contribute to the understanding for the reader, but is still relevant in order to support particular claims made in the report (for instance a purely mathematical derivation), should be put in the appendix. (That is, only if it cannot be found elsewhere. Otherwise a simple citation suffices.)

%For the rest the appendices are like the other chapters, i.e. they can have sections, figures, tables, and citations (even though the appendix comes after the list of references).

\section{Scenarios}
The following task scenarios were given to participants of the first iteration user studies. The link leads to the original prototype that was used.

\subsection{Scenario 1}
\begin{itemize}
  \item End goal: Let colleague review changes
  \item Estimated time: 8 mins
  \item Link: https://marvelapp.com/c89590
\end{itemize}

A colleague (Firstname Lastname) has sent you a link to a lesson.
She informed you that the second item in the vocabulary (write) exercise has the wrong speaker role (should be F1) and also should be added to the review manager. 
She asked you to correct the error and afterwards allow her to review your changes. 
Make sure you’re not editing the live content.

\subsection{Scenario 2}
\begin{itemize}
  \item End goal: Publishing changed content
  \item Estimated time: 4 mins
  \item Link: https://marvelapp.com/1011fjj
\end{itemize}

A colleague (Firstname Lastname) has changed a lesson within the German language package.
She asked you to review the changes. 
Look at the changes she made and if you don’t find any errors make them available to the Babbel end-user.

\subsection{Scenario 3}
\begin{itemize}
  \item End goal: Eliminating error and save
  \item Estimated time: 6 mins
  \item Link: https://marvelapp.com/102f4b4
\end{itemize}

A translator (user name: rcarlos) is currently working on a localization of German lessons (to Portuguese). 
Recently a translated exercise was published, but according to customer service users have complained that there is a translation missing within this exercise. 
Find the exercise which has been translated and locate the item with the missing translation. 
Add the translation and save your changes.

\section{Pre-session Questionnaire} \label{append:presession-quest-1}

\begin{table}[h!]
\begin{tabular}{|l|p{3cm}|p{1.5cm}|p{2cm}|p{3cm}|}
\hline
{\bf User} & {\bf Familiar with version control?} & {\bf Used it?} & {\bf Experience with current tool} & {\bf Used other content management or authoring systems?} \\ \hline
1                 & No                                        & No                       & 1 - 3 years                        &                                                        \\ \hline
2                 & No                                        & No                       & 1 - 3 years                        &                                                        \\ \hline
3                 & No                                        & No                       & 3 months - 1 year                  & WordPress                                              \\ \hline
4                 & No                                        & No                       & more than 3 years                  &                                                        \\ \hline
5                 & No                                        & No                       & 1 - 3 years                        &                                                        \\ \hline
\end{tabular}
\centering
\caption{Pre-session questionnaire}
\label{table:pre-sess-quest}
\end{table}