\chapter{Introduction}
\label{chap:introduction}

Below you find an example of an introduction structure. See \cite{Leferink12,Meijerink12} for more extensive hints on writing.

\section{Motivation}
\label{sec:motivation}
What is the relevance of the presented work, and what is the relation to previous work done in this field?

\section{Framework}
\label{sec:framework}
Where was the presented research carried out, and to what project(s) is it related? 

Possibly this section is combined with the first section, particularly if the presented work is directly motivated by previous work done in the same group. 

\section{Goal(s) of the assignment/Research question(s)}
\label{sec:goal}
What is aimed to be achieved by this work? Or: what is the particular question that is answered by this report? 

This section should be short and very specific. 

Possibly several distinct research questions are formuled as a numbered list, but: the smaller the number of questions, the better. 

\section{Report organization}
\label{sec:organization}
This section describes the structure of the report. It consists of one paragraph, listing the \emph{purposes} of the individual chapters (and nothing else), for instance: 

The remainder of this report is organized as follows. In Chapter~\ref{chap:body}, blabla .... Then, in Chapter~YY, ... Finally, in Chapter~\ref{chap:conclusions}, conclusions and recommendations are given.

Note that appendices are not described here, and that the word 'Chapter' is capitalized when it is followed by a number.

The chosen structure should either be a common one, or follow from the foregoing sections in an obvious way. If necessary, one might consider adding one more section between the goal and report organization, describing the rough approach.


\section{Technical level of the introduction}

The introduction chapter should not be too technical, i.e. equations, graphs, and technical drawings should preferably be postponed to later chapters, unless they directly form the core motivation of the work. The technical level of the introduction should be such that the relevance, goal, and logic of the report structure are clear. Possibly refer to later chapters for technical details, in order to reassure the reader.
